### 2018-06-29 doc/plos/text/manuscript.tex
add related work subsection

@@

>>>>

\subsection*{Related Work}

An approach often used to address some of these issues is to incorporate novel
data streams (NDS) \cite{althouse2015enhancing}. These signals, when based on
search queries \cite{eysenbach2006infodemiology, polgreen2008using,
hulth2009web, ginsberg2009, dugas2013, araz2014using, santillana2014can,
preis2014adaptive}, social media \cite{ritterman2009, culotta2010towards,
signorini2011use, achrekar2011predicting, broniatowski2013national,
paul2014twitter}, information-seeking behavior \cite{generous2014global,
mciver2014wikipedia, hickmann2015forecasting}, and participatory surveillance
\cite{smolinski2015flu, chunara2013flu}, are collectively termed ``digital
surveillance'', as opposed to traditional surveillance of which wILI is one
example. Although many of these signals are available with little to no lag,
each has distinct shortcomings, and it seems that common practice has been to
nowcast wILI using any one of the available digital surveillance signals in
isolation. However, it was more recently demonstrated that multiple digital
surveillance signals can be used in parallel to produce more accurate nowcasts
of national wILI \cite{santillana2015combining}.

@@

\bibitem{althouse2015enhancing}
Althouse BM, Scarpino SV, Meyers LA, Ayers JW, Bargsten M, Baumbach J, et~al.
\newblock Enhancing disease surveillance with novel data streams: challenges
  and opportunities.
\newblock EPJ Data Science. 2015;4(1):1--8.

\bibitem{eysenbach2006infodemiology}
Eysenbach G.
\newblock Infodemiology: tracking flu-related searches on the web for syndromic
  surveillance.
\newblock In: AMIA Annual Symposium Proceedings. vol. 2006. American Medical
  Informatics Association; 2006. p. 244.

\bibitem{polgreen2008using}
Polgreen PM, Chen Y, Pennock DM, Nelson FD, Weinstein RA.
\newblock Using internet searches for influenza surveillance.
\newblock Clinical infectious diseases. 2008;47(11):1443--1448.

\bibitem{hulth2009web}
Hulth A, Rydevik G, Linde A.
\newblock Web queries as a source for syndromic surveillance.
\newblock PloS one. 2009;4(2):e4378.

\bibitem{ginsberg2009}
Ginsberg J, Mohebbi MH, Patel RS, Brammer L, Smolinski MS, Brilliant L.
\newblock Detecting influenza epidemics using search engine query data.
\newblock Nature. 2009;457(7232):1012--1014.

\bibitem{dugas2013}
Dugas AF, Jalalpour M, Gel Y, Levin S, Torcaso F, Igusa T, et~al.
\newblock Influenza Forecasting with Google Flu Trends.
\newblock {PLoS} {ONE}. 2013;8(2):e56176.
\newblock doi:{10.1371/journal.pone.0056176}.

\bibitem{araz2014using}
Araz OM, Bentley D, Muelleman RL.
\newblock Using Google Flu Trends data in forecasting influenza-like--illness
  related ED visits in Omaha, Nebraska.
\newblock The American journal of emergency medicine. 2014;32(9):1016--1023.

\bibitem{santillana2014can}
Santillana M, Zhang DW, Althouse BM, Ayers JW.
\newblock What can digital disease detection learn from (an external revision
  to) Google Flu Trends?
\newblock American journal of preventive medicine. 2014;47(3):341--347.

\bibitem{preis2014adaptive}
Preis T, Moat HS.
\newblock Adaptive nowcasting of influenza outbreaks using Google searches.
\newblock Royal Society open science. 2014;1(2):140095.

\bibitem{ritterman2009}
Ritterman J, Osborne M, Klein E.
\newblock Using prediction markets and Twitter to predict a swine flu pandemic.
\newblock In: 1st international workshop on mining social media. vol.~9. ac.
  uk/miles/papers/swine09. pdf (accessed 26 August 2015); 2009. p. 9--17.

\bibitem{culotta2010towards}
Culotta A.
\newblock Towards detecting influenza epidemics by analyzing Twitter messages.
\newblock In: Proceedings of the first workshop on social media analytics. ACM;
  2010. p. 115--122.

\bibitem{signorini2011use}
Signorini A, Segre AM, Polgreen PM.
\newblock The use of Twitter to track levels of disease activity and public
  concern in the US during the influenza A H1N1 pandemic.
\newblock PloS one. 2011;6(5):e19467.

\bibitem{achrekar2011predicting}
Achrekar H, Gandhe A, Lazarus R, Yu SH, Liu B.
\newblock Predicting flu trends using twitter data.
\newblock In: Computer Communications Workshops (INFOCOM WKSHPS), 2011 IEEE
  Conference on. IEEE; 2011. p. 702--707.

\bibitem{broniatowski2013national}
Broniatowski DA, Paul MJ, Dredze M.
\newblock National and local influenza surveillance through Twitter: an
  analysis of the 2012-2013 influenza epidemic.
\newblock PloS one. 2013;8(12):e83672.

\bibitem{paul2014twitter}
Paul MJ, Dredze M, Broniatowski D.
\newblock Twitter improves influenza forecasting.
\newblock PLoS currents. 2014;6.

\bibitem{generous2014global}
Generous N, Fairchild G, Deshpande A, Del~Valle SY, Priedhorsky R.
\newblock Global disease monitoring and forecasting with Wikipedia.
\newblock PLoS Comput Biol. 2014;10(11):e1003892.

\bibitem{mciver2014wikipedia}
McIver DJ, Brownstein JS.
\newblock Wikipedia usage estimates prevalence of influenza-like illness in the
  United States in near real-time.
\newblock PLoS Comput Biol. 2014;10(4):e1003581.

\bibitem{hickmann2015forecasting}
Hickmann KS, Fairchild G, Priedhorsky R, Generous N, Hyman JM, Deshpande A,
  et~al.
\newblock Forecasting the 2013--2014 influenza season using Wikipedia.
\newblock PLoS Comput Biol. 2015;11(5):e1004239.

\bibitem{smolinski2015flu}
Smolinski MS, Crawley AW, Baltrusaitis K, Chunara R, Olsen JM, W{\'o}jcik O,
  et~al.
\newblock Flu Near You: Crowdsourced Symptom Reporting Spanning 2 Influenza
  Seasons.
\newblock American journal of public health. 2015;105(10):2124--2130.

\bibitem{chunara2013flu}
Chunara R, Aman S, Smolinski M, Brownstein JS.
\newblock Flu near you: an online self-reported influenza surveillance system
  in the USA.
\newblock Online Journal of Public Health Informatics. 2013;5(1).

\bibitem{santillana2015combining}
Santillana M, Nguyen AT, Dredze M, Paul MJ, Nsoesie EO, Brownstein JS.
\newblock Combining search, social media, and traditional data sources to
  improve influenza surveillance.
\newblock PLoS Comput Biol. 2015;11(10):e1004513.
